\chapter{On quantitative imaging of single cells}
\label{imaging:introduction}

\section{Introduction}

Fluorescence microscopy is a
powerful tool for measuring single-cell properties, especially when sub-cellular
spatial resolution is required. With modern computing
power and robotics, we can now use this technology to amass large
quantities of image data and so study
cell biology with increasing breadth and depth. 
Accurate high-throughput imaging and image analysis of single-cell data across
large numbers of conditions is becoming routine in
some labs and will continue to become even more commonplace
as the technology simultaneously improves and becomes cheaper.
The availability of the technology has led, in recent years, to a boom
in large-scale microscopy studies of single-cell phenotypes
\cite{Neumann2006,Young2008,Feng2009,Houle2010,Held2010,Singh2010,Futamura2012}.
However, our ability to generate
microscopy data is outpacing our collective ability to
analyze and interpret it.


Fluorescence microscopy has been an experimental staple of biology for many years,
though it is still infrequently used for rigorous quantitative analysis. More often,
researchers use fluorescence imaging to demonstrate a particular phenotype
(as I do in \ar{fig:insulation:schematic}),
or to manually count the instances of a visually obvious
phenotype. Our own visual perception is notoriously prone to error, however,
as our brains can choose to perceive patterns that do not exist, thus
allowing for latent biases to affect how we manually tally the data.
As biologists we are often painfully aware of this problem,
and so there seems to be a general unease when it comes
to evaluating imaging data. We all know the joke that,
in published figures, ``representative image'' is a euphemism for
``the best image I could find.''


The distrust is understandable, as proper evaluation
of imaging data is a non-trivial task, and researchers
rarely publish enough details to even allow
for thorough evaluation in the first place. This problem is 
made worse by a lack of imaging and analysis standards, and by the
difficulty inherent to making large image-datasets publicly available.


Biological image
quantification is a difficult and generally unsolved problem \cite{Danuser2011},
and its various approximate
solutions tend to require a level of expertise in mathematics
and computer programming, and at least a cursory
understanding of microscopy optics. Importantly, it also requires expertise
in the experimental biology under study. Few, if any, biology training
programs prepare students for such broad practical knowledge.


Cell biologists, like myself,
are rarely trained in quantitative fields
and so we tend to rely on our colleagues
in analytical fields to do the quantitative work for us. Those analysts,
in turn, typically lean back on the biologists for understanding the
``what'' and ``why'' of the analysis.
Unfortunately, the large knowledge and language
asymmetry between biologists and analysts
creates steep communication barriers that are hard to break
down. Therefore, the full benefits to cell biology of careful
quantitative microscopy may be going untapped.


My own work relies almost entirely on imaging (\ar{insulation:introduction})
and, having spent so much time thiking about and performing image analysis,
I have come to prefer imaging over other methods not only for its efficiency
in measuring single-cell properties across large numbers
of conditions, but also because it provides a literal view into
the mysterious and beautiful world of the cell. I therefore hope that
careful single-cell image analysis will someday become as commonplace as Western
blots.


My overarching goal in writing this chapter is to provide
an image analysis resource that is both accessible
to classically trained biologists
and useful for analysts from non-biological fields
that may be preparing to move into the field. In general, I aim to provide careful
biological and analytical
reasoning for a subset of the many choices that must
be made with respect to
fluorescence imaging experiments. In specific, I focus
on dealing with
experimental and imaging artifacts and noise,
and how to choose biologically meaningful single-cell
measurements. The methods and rationale in this chapter
are used extensively in \ar{insulation:introduction}.



\input{TEXT/imaging/model}

\input{TEXT/imaging/correction}

\input{TEXT/imaging/features}

\input{TEXT/imaging/variation}

\input{TEXT/imaging/discussion}

\input{TEXT/imaging/methods}
