
\newacronym{atp}{ATP}{Adenosine tri-phospate}

\newacronym{tcf}{TCF/Lef}{T-Cell Factor/Lymphoid enhancer-binding factor. \bcat\ co-factors}

\newacronym{tgfbsf}{TGFB$_\text{sf}$}{Transforming Growth Factor Beta superfamily}

\newacronym{tgfb}{\tgf}{Transforming Growth Factor Beta (ligand)}

\newacronym{bmp}{BMP}{Bone Morphogenic Protein (ligand). A family within \tgfbsf}

\newacronym{gdf}{GDF}{Growth and Differentiation Factor (ligand). A family within \tgfbsf}

\newacronym{alk}{ALK}{Activin receptor-Like kinase. Type I \tgfbsf\ receptors}

\newacronym{jup}{JUP}{Junctional Plakoglobin (\textgamma{catenin}). Paralog of \bcat}

\newacronym{bcat}{CTNNB1}{Catenin, Beta 1 (\bcat). Transcription factor activated by canonical Wnt signaling}

\newacronym{fzd}{FZD}{Frizzled. Receptor for Wnts}

\newacronym{mh1}{MH1}{MAD homology 1. DNA-binding domain of the rSmad proteins}

\newacronym{mh2}{MH2}{MAD homology 2. Protein-binding domain of the rSmad proteins}

\newacronym{dpp}{DPP}{Decapentaplegic. The \glspl{fly} ortholog of BMP2/4}

\newacronym{arm}{arm}{Armadillo. The \glspl{fly} ortholog of \bcat}

\newacronym{mad}{MAD}{Mothers Against DPP. The \glspl{fly} ortholog of the rSmads}

\newacronym{g1}{G1}{Growth phase 1. The phase of the cell cycle in which
cells have normal diploid (2N) DNA content.}

\newacronym{g2}{G2}{Growth phase 2. The phase of the cell cycle in which
cells have twice-normal (4N) DNA content.}

\newacronym{rsmad}{rSmad}{receptor-Smad}

\newacronym{ismad}{iSmad}{inhibitory-Smad. Comprises Smad6/7}

\newacronym{bsmad}{bSmad}{BMP-specific rSmad. Comprises Smad1/5/8}

\newacronym{tsmad}{tSmad}{\tgf-specific rSmad. Comprises Smad2/3}

\newacronym{rrna}{rRNA}{ribosomal RNA. E.g. 18S rRNA used in qPCR controls}

\newacronym{qpcr}{qPCR}{quantitative PCR. Method for measuring relative RNA abundance}

\newacronym{sirna}{siRNA}{small interfering RNA.
Short RNAs (22-24 bases) used to reduce a target
RNA abundance via the cellular RNA-interference machinery}

\newacronym{mrna}{mRNA}{messenger RNA}

\newacronym{ip}{IP}{Immunopreciptiation. A standard biochemical technique in which an antibody is used to capture a target protein}

\newacronym{coip}{co-IP}{co-Immunopreciptiation. An IP, except that proteins different from the original target are then assayed. If a protein can co-IP with another protein, this is taken as evidence that they physically interact}

%\newacronym{bio}{BIO}{6-bromoindirubin-3'-oxime. An ATP analog that inhibits \gsk\ with decent specificity}

\newacronym{I}{$I$}{Mathematical symbol representing an image}

\newacronym{F}{$F$}{Mathematical symbol representing a foreground fluorescence layer in an image}

\newacronym{B}{$B$}{Mathematical symbol representing a background fluorescence layer in an image}

\newacronym{D}{$D$}{Mathematical symbol representing the baseline detector value in a fluorescence image}

\newacronym{S}{$S$}{Mathematical symbol representing the shading term in a fluorescence image}

\newacronym{sigma}{s.d.}{ The standard deviation of a set of values}

\newacronym{cv}{$cv$}{ The coefficient of variation. Defined as standard deviation over the mean}

\newacronym{tgfbr}{TGFBR1-3}{TGFB receptors, types 1 through 3}

\newacronym{bmpr}{BMPR1/2}{BMP receptors, types 1 and 2}

\newacronym{acvr}{ACVR1/2}{Activin A receptors, types 1 and 2}

\newacronym{gpcr}{GPCR}{G-protein coupled receptor. 7-pass transmembrane
    receptors that signal through hetero-trimeric G-proteins}

\newacronym{lrp}{LRP5/6}{Low-density lipoprotein receptor-related protein 5 and 6.
    Wnt ligand co-receptors}

\newacronym{dkk}{DKK1}{Dikkopf-1. An extracellular Wnt antagonist}

\newacronym{rspo}{RSPO1}{R-spondin 1. An extracellular Wnt co-factor}

\newacronym{lgr}{LGR4/5}{Leucine-rich repeat-containing G-protein coupled receptors
4 and 5. RSPO1 receptors and Wnt co-receptors}

\newacronym{tcf}{TCF/Lef}{T-cell factor/Lymphoid enhancer-binding factor. Family of
    \bcat\ transcriptional co-factors}

\newacronym{ror}{ROR1/2}{Receptor tyrosine kinase-like orphan receptors 1 and 2.
    Receptors of non-canonical Wnt5A}

\newacronym{ec50}{EC$_{50}$}{Half-maximal effective concentration.}
%\newacronym{}{}{}
%\newacronym{}{}{}
%\newacronym{}{}{}
%\newacronym{}{}{}
%\newacronym{}{}{}




\glsunsetall % Makes it so that first appearance of acroynyms are not expanded.