\chapter{On cellular signaling}
\label{introduction:introduction}

\section{Introduction}

Both in the context of multi-cellular and single-celled
organisms, cells are constantly
challenged to stay alive and perform
tasks in the face of unpredictable environmental
changes. For single-cell organisms these changes
can be particularly dramatic, as the external temperature,
osmolarity, and other properties are outside of cellular
control \cite{Bennett2008,Acar2008}.
For cells within multi-cellular organisms,
microenvironmental changes fluctuate much less due to
controlled modification of the environment by neighboring
cells. However, in order to exert control over the environment,
cells must constantly communicate with one another. The
messages sent from cell to cell are themselves a form
of unpredictable environmental change that cells must deal with.
Here, I focus on this latter problem. That is, how do
cells within multi-cellular organisms accurately interpret
messages sent from their neighbors?


The potential variety of cellular signals that cells face
is explosively large \cite{Natarajan2006},
and yet cells must somehow be able to tell these signals apart.
Mammalian cells must generally be able to respond
to changes within a highly complex biochemical milieu that contains
proteins, small molecules, and ions.
Adult stem cells must be able to reliably
divide and make differentiation decisions so as to
recreate functional units of organs. Embryonic
stem cells must be able to generate entire organisms,
going from a single cell to billions that each have different
functional and morphological properties. And those embryonic stem cells must perform this
task with extreme accuracy, since even a small error at the early
stages would be compounded through the developmental process \cite{Balazsi2011}.


It is amazing that cells can respond to such an unpredictable, complex, and
ever-changing environment. Even more amazing is that they do so
using the interactions between finite numbers
of molecules, both in quantity and type, to perform computational tasks.
In order for cells to be so responsive, they must first be
able to recognize that the environment has changed: they must have
sensors. In order for a cell to ``understand'' what has happened,
it must convert the influx of
sensory information into an internal model of its environment.
Finally, cells must map that model
onto a decision regarding what action to take in response. I refer
to the first part of this process, the conversion of external
information into an internal model, as ``signal transduction'' or, in
short, ``signaling.'' The second
part, the conversion of the internal model into a behavior, I refer
to as ``cellular decision-making.''


Understanding how cells make
decisions, as a consequence of environmental or
pathological perturbation, is at the core of cell biology.
In experimental cell biology, we purposely break the ability of a cell
to accurately process information,
or its ability to make a correct decision after processing that information,
in order to understand the
decision-making process. A cell, on the other hand, may
``unintentionally'' break those same processes, thus
resulting in pathology.
If we can understand the basis of cellular signaling and decision-making,
then we can intervene to correct such pathologies.
In this way, we hope that discoveries made in basic biology will eventually
show utility in the clinical treatment of human patients.


Cellular signaling is difficult to study, and so the degree
of uncertainty in even the best-studied systems is astonishing (as exemplified in
\ar{pathways:introduction}).
In this chapter, I outline an abstraction of the problem of cellular
signaling to give some perspective on why it is so difficult to understand.
This same abstract framework can be used to rigorously
define cell biological problems, and thus serves as a tool
for designing meaningful experiments.
By approaching the problem of cellular signal processing in this way,
we become more able to directly
answer the most basic questions in cell biology: what signals
do cells ``listen to,'' how do they model these signals internally, and how
do they use those models to make decisions?






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{TEXT/introduction/canon}

\input{TEXT/introduction/hierarchy}

\input{TEXT/introduction/encoding}

\input{TEXT/introduction/encodingSolution}

\input{TEXT/introduction/aims}