\chapter[On Wnt and the TGFB superfamily]{On Wnt and the Transforming Growth Factor Beta superfamily}
\label{pathways:introduction}

\section{Introduction}


The signaling components of the 
Transforming Growth Factor Beta 
superfamily (\tgfbsf) and Wnt pathways are deeply conserved across metazoa.
Further, they are often active in the same
tissue compartments at the same time, yielding ample opportunity
for these pathways to interact.
Indeed, stem cells in many systems integrate signals from
these two major pathways to make fate decisions. In the language
of \ar{introduction:introduction}, cells must encode some
properties of the external Wnt and \tgfbsf\ ligands into internal models
that can be subsequently mapped onto a cellular decision (such as differentiation).
For the Wnt and \tgfbsf\ pathways the encoded property
is thought to be concentration. In other words,
it is the ligand concentration that carries information; it
is this aspect of the signal that the cells eventually convert into a decision.
This dose-dependent
encoding mechanism is what classifies the \tgfbsf\ and Wnt ligands as
classical ``morphogens.''


Wnt and \tgfbsf\ have been extensively studied for decades, yet many
uncertainties remain \cite{Li2012,Hernandez2012,Massague2012}.
The uncertainties stem in part from the extensive redundancy
found in these pathways: each signaling component is represented by
anywhere from
one to over twenty distinct gene products. This redundancy makes classical
analysis by genetic ablation difficult, as many genes would have to be
ablated simultaneously. Additionally, these pathways are central to
mammalian development, and so to study them in the adult requires
inducible genetic constructs. Further, each pathway shows extensive
context-dependency in its behavioral output, so that finding general 
signaling principles has been no trivial task. Finally, 
many of the most-studied output behaviors
are temporally far removed from the initial signaling
events. As discussed in \ar{introduction:introduction}, such distant
temporal connections between network nodes makes the assignment of
meaningful cellular functions quite difficult.


Even less understood is how
cells combine information from the Wnt and \tgfbsf\ pathways to make fate
decisions. While a body of literature exists on this topic, no
context-independent mechanisms of pathway integration have been
uncovered. Is it true then that
``the context, more than the proteins \ldots\
is what shapes the response \cite{Massague2012}''? Or, as I suggested in
\ar{introduction:introduction}, are there simpler principles of
crosstalk that are being hidden by overly-complex models of signaling
crosstalk?


Before answering that question in \ar{insulation:introduction},
in this chapter I review the \tgfbsf\ (\autoref{pathways:tgfb})
and Wnt pathways (\autoref{pathways:wnt}). This review should provide the background
necessary to understand how signals and responses are thought to be encoded
by these pathways. I also discuss the putative mechanisms of cross-pathway
signal integration so far discovered in the field
(\ar{pathways:wntTgfb:mechanism}), and how to make sense of those
results in the conceptual context of \ar{introduction:introduction}.


As a reminder, I narrowly define ``signaling'' as the process of converting
an extracellular signal into an internal model of that signal, and I define
``cellular decision-making'' as the use of that internal model to affect
a behavioral change. Bear in mind that this distinction is not used in the
majority of the literature, and so much of the work presented here conflates
these two processes. This is important, since I believe that this conflation
has led to inaccurate inferences regarding the integration of signaling events.
All together, this chapter paves the way for the primary
claim of this dissertation, that the Wnt and \tgfbsf\ pathways
are insulated from one another during signal transduction.


\subsubsection{Nomenclature}

I refer to genes from
multiple organisms throughout this chapter. There are differences
in standardized writing conventions for gene and protein names between organisms, so
to minimize confusion I adopt one convention for all species. I refer
to the protein products of genes using all-uppercase for
symbols or initial capitals for full protein names. To refer to a protein
family, I drop the alphanumeric identifier associated with individual members.
For example, the Frizzled (FZD) protein family contains the member Frizzled-1
(FZD1). Finally, note that the TGFB superfamily shares its name with
one of the families contained within it, the
prototypical \tgf\ family (as discussed below).
For clarity, I add a subscript and use the Latin `B'
when referring to the TGFB superfamily (\tgfbsf); I drop the subscript 
and use the Greek `\textbeta' when
referring specifically to the \tgf\ family.


\input{TEXT/pathways/tgfb}

\input{TEXT/pathways/wnt}

\input{TEXT/pathways/wntTgfb_function}

\input{TEXT/pathways/wntTgfb_mechanism}

\input{TEXT/pathways/discussion}

\input{TEXT/pathways/methods}